Modeling the Food Insecurity Experience Scale (FIES) in the Present and Future

### 2020-09-02 docs/modeling_fies_v2.tex
Updates from Overleaf

\affil[1]{T.H. Chan School of Public Health, Harvard University}
\affil[2]{TU Wien}

@@

\subsection{Covariates Available in the Present and Future}
To model the FIES in the future, we use projections derived in line with the Shared Socio-Economic Pathways (SSPs).  The SSPs are a framework to estimate what the future might look like in terms of human development and climate-change mitigation, based on a number of scenarios.  We use projections of GDP \cite{Dellink2017}, education \cite{KC2017}, and urbanization \cite{Jiang2017} for SSP2, the middle-of the road pathway.

@@

%Determine local environment
\bibliography{C://Users/matt/library}

>>>>

\affil[1]{T.H. Chan School of Public Health, Harvard University}
\affil[2]{Department of Economics, Vienna University of Economics and Business}

@@

\begin{table}[H]
	\begin{tabular}{llll}
		\toprule
		Name & Availability & Scale & Source \\
		\midrule
        HDI & Annual & Subnational & GDL \\
        Life Expectancy & Annual & Subnational & GDL \\
        GNI Per Capita & Annual & Subnational & GDL \\
        Expected Years School & Annual & Subnational & GDL \\
        Mean Years School & Annual & Subnational & GDL \\
        Country Programmable Assistance (CPA) & Annual & National & OECD Database \\
        AG PCT GD & Annual & National & World Bank \\
        Import Value Per Capita & Annual & National & World Bank \\
        Undernourishment & Annual & National & World Bank, FAO \\
        government_effectiveness & Annual & National & World Bank WGIs \\
        control_corruption & Annual & National & World Bank WGIs \\
        regulatory_quality & Annual & National & World Bank WGIs \\
        rule_of_law & Annual & National & World Bank WGIs \\
        stability_noviolence & Annual & National & World Bank WGIs \\
        voice_accountability & Annual & National & World Bank WGIs \\
        mean annual precip & static & subnational & WorldClim \\
        mean average temp & static & subnational & WorldClim \\
        forest cover & 2016 & subnational & Song et al \\
        elevation & static & subnational & ETOPO5 \\
        ruggedness & static & subnational & ETOPO5 \\

        %TODO:
        %Nutritional Diversity
        %Malaria
        %Stunting
        %Livestock
        %Buitup
        %Irrigation
        %TTC
        %Sum of conflict deaths
        %Urban-Rural pop

		\bottomrule
	\end{tabular}
	\caption{Co-Variates Included in Present-Day Analysis NEW}
	\label{tab:covars2}
\end{table}

\subsection{Covariates Available in the Present and Future}
To model the FIES in the future, we use projections from multiple sources. Most covariates are derived in line with the Shared Socio-Economic Pathways (SSPs). The SSPs are a framework to estimate what the future might look like in terms of human development and climate-change mitigation, based on a number of scenarios.  We use projections for SSP2, the middle-of the road pathway, from \cite{Crespo2017}, \cite{Dellink2017}, \cite{Rao2019a}, \cite{KC2017}, \cite{Jiang2017} and \cite{SSPData2017}.
Additionally, we use projections for poverty and water scarcity from \cite{WDL2020PC} and \cite{WDL2020WSC} respectively and estimate our own forecasts (with elasticities to GDP) for ``Imports per capita'' and ``Agriculture as a Percent of GDP'' (See Table \ref{tab:covars3}.

\begin{table}[H]
	\begin{tabular}{llll}
		\toprule
		Name & Availability & Scale & Source \\
		\midrule
		GDP PPP per capita & Annual & National & \cite{Crespo2017} \\
		- & - & - & \cite{Dellink2017} \\
		Gini index & Annual & National & \cite{Rao2019a} \\
		Share primary education & Annual & National & \cite{KC2017} \\
		Share secondary education & Annual & National & \cite{KC2017} \\
		%Share tertiary education & Annual & National & \cite{KC2017} \\
		Share people in urban areas & Annual & Subnational & \cite{Jiang2017} \\
        Crops production & Annual & Regional & \cite{Jiang2017} \\
        Cropland cover & Annual & Regional & \cite{SSPData2017} \\
        Forest land cover & Annual & Regional & \cite{SSPData2017} \\
        Built up land cover & Annual & Regional & \cite{SSPData2017} \\
        Livestock production & Annual & Regional & \cite{SSPData2017} \\
        Poverty headcount index & Annual & National & \cite{WDL2020PC} \\
        %Water stress index & Annual & Subnational & \cite{WDL2020WSC} \\
        Water scarcity index & Annual & Subnational & \cite{WDL2020WSC} \\
        %Absolute water scarcity index & Annual & Subnational & \cite{WDL2020WSC} \\
        Imports per capita & Annual & National & \cite{TheWorldBank2016} \\
        Agriculture percent of GDP & Annual & National & \cite{TheWorldBank2016} \\
        \bottomrule
	\end{tabular}
	\caption{Co-Variates Included in Forecast Analysis}
	\label{tab:covars3}
\end{table}

@@

%Determine local environment
\bibliography{references}
